Code walkthrough

### 2022-10-07 src/explore_aghq/walkthrough.Rmd
Walkthrough of sample_marginal.marginallaplace finished

```{r}
simlist$lambda <- exp(quad$normalized_posterior$nodesandweights$logpost_normalized) * quad$normalized_posterior$nodesandweights$weights
simlist$lambda
```

@@

```{r eval=FALSE}
j <- apply(stats::rmultinom(M, 1, simlist$lambda), 2, function(x) which(x == 1))
j

@@

#' For each element of the list, create a matrix with d rows (and 1 column? always?)
Z <- lapply(A_split, matrix , nrow = d)
```

>>>>

```{r}
simlist$lambda <- exp(quad$normalized_posterior$nodesandweights$logpost_normalized) * quad$normalized_posterior$nodesandweights$weights
head(simlist$lambda)
```

@@

```{r}
j <- apply(stats::rmultinom(M, 1, simlist$lambda), 2, function(x) which(x == 1))
length(j) #' Should be M
j

@@

#' For each element of the list, create a matrix with d rows (and 1 column? always?)
Z <- lapply(A_split, matrix , nrow = d)
str(Z)
```

In the code there is now a big call to `mapply`, which we are going to break down step-by-step.
First set the inital values that `function(.x, .y)` will iterate over:

```{r}
.x <- Z[[1]]
str(.x)

.y <- names(Z)[[1]]
str(.y)
```

Now solve the equation `L %*% .z = .x` for `.z`

```{r}
.z <- solve(simlist$L[[as.numeric(.y)]], .x)
str(.z)
```

Now add the mode (where the additional manipulation is so that if there are multiple samples from the same `j` then there will be the corresonding number of columns):

```{r}
.z <- .z + do.call(cbind, rep(list(simlist$mode[[as.numeric(.y)]]), ncol(.x)))
str(.z)
```

Do this using a `mapply` call:

```{r}
samps <- mapply(
  function(.x, .y) as.numeric(solve(simlist$L[[as.numeric(.y)]], .x)) + do.call(cbind, rep(list(simlist$mode[[as.numeric(.y)]]), ncol(.x))),
  Z,
  names(Z),
  SIMPLIFY = FALSE
)

#' Order them properly
#' My guess is that you'd want them to be ordered according to how j was drawn, rather
#' than being grouped up by the value of lambda
ord <- numeric(length(j))
cumtab <- cumsum(c(0, tt))
cumtab <- cumtab[-length(cumtab)]
cnt <- numeric(length(unique(j)))
names(cnt) <- sort(unique(j))

for (i in 1:length(j)) {
  wc <- which(names(cnt) == j[i])
  cnt[wc] <- cnt[wc] + 1
  ord[i] <- cumtab[wc] + cnt[wc]
}

samps <- Reduce(cbind, samps)
samps <- samps[, ord]
samps
```

```{r}
#' This is now the length of the fixed effects
d <- length(quad$optresults$mode)

#' Just so that we can get the names of the theta (fixed effects)
thetanames <- colnames(quad$normalized_posterior$nodesandweights)[1:d]
theta <- simlist[j, thetanames]

#' In one dimension, R's indexing is not type consistent
if (!is.matrix(samps)) {
  samps <- rbind(samps)
  rownames(samps) <- NULL
}

if (!inherits(theta, "data.frame")) theta <- data.frame(theta1 = theta)

out <- list(
  samps = samps,
  theta = theta
)

out$theta

# Add the marginals for theta, with possible transformation
class(quad) <- "aghq" #' This is preventing sample_marginal.marginallaplace being used
out$thetasamples <- sample_marginal(quad, M, transformation, interpolation)
str(out)
```
